Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
PARAGRAPH ARGUES ABOUT THE CONCRETE APPLICATION OF TOPIC MODELLING AND LABELLED TOPIC EXTRACTION IT NEEDS TO BE TIGHTER BUT IT ALSO NEEDS TO BE HERE

@@

\todo[inline]{We still haven't shown that topics are useful -- a reviewer comment}

>>>>

%%%% THIS PARAGRAPH ARGUES ABOUT THE CONCRETE APPLICATION OF 
%%%% TOPIC MODELLING AND LABELLED TOPIC EXTRACTION
%%%% IT NEEDS TO BE TIGHTER BUT IT ALSO NEEDS TO BE HERE
There are many practical applications of topic modelling and \emph{labelled  topic extraction}.
These methods are useful for providing overviews of development.
We can improve project dashboards, used by managers, by showing both the current topics of development as well those that relate to NFRs.
Some quality assurance questions can be addressed by seeking evidence within repositories that NFR related topics are being addressed.
Topic modelling can be used to check if development is on track and focused.
% This is a very long example it'd be nice if it was tighter
Perhaps development has been sidetracked by cascading issues that appeared during implementation.
For instance, a developer adding an optimization to a RDBMS might have to change multiple modules in order to provide that optimization code with enough information to operate. 
This issue might trigger a series of cascading changes that might be difficult to discover when trying to explain why the project's release date has been missed. 
Labelled Topic extraction could be used to detect this distinct focus of development.

@@

%\todo[inline]{We still haven't shown that topics are useful -- a reviewer comment}
